---
title: "The Neptunes Clean UP"
author: "Shaniece Gooden"
date: "2023-05-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I did a little more digging (Google searches) and found that some of the titles in the initial list of songs produced by Pharrell Williams contained songs where he was actually a writer and not a producer. This mistake could be made given that Pharrell and The Neptunes are usally co-producers and co-writers on songs rather than just one or the other. Thus I separated out the songs that were on the Billboard Hot 100 list and researched to ensure all the songs were actually produced by The Neptunes or Pharrell Williams. 
```{r}
library(tidyverse)
library(janitor)

#Pull out rows where song is on Billboard Hot 100
bill_y_nep <- The_Neptunes_N_E_R_D |>
  clean_names() |>
  filter(billboard_hot_100_single=="Y")
bill_y_nep
```
All the songs on the Billboard Hot 100 for The Neptunes were in fact produced by The Neptunes.

```{r}
bill_y_pw <- Pharrell_Williams |>
  clean_names() |>
  filter(billboard_top_100 == "Y")
bill_y_pw
```

There were 7 songs that Pharrell Williams did not actually produce but was a co-writer.The following songs need to be removed:
"Rump Shaker"
"Hella Good"
"Get Lucky"
"Heatstroke"
"Havana"
"Skeletons"
"Buss It"

